Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-23 article/article.Rmd
Commit 2024-05-23 19:10

```{r relative-month-occurancies, echo=FALSE, fig.cap="Statistics of the number of CE occurancies for each month. The box represents the values of the low $25\\,\\%$ percentile to $75\\,\\%$ percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean."}
knitr::include_graphics("../images/clim_CE_month_norm_MAX_median_N-2.png")
```
<!--
```{r echo=FALSE, fig.cap="Distribution of the number of CE cases"}
knitr::include_graphics("../images/climCEmonth-1.png")
```
--->

@@

... @Zhang2018 ....

```{r echo=FALSE, fig.cap="Relation of mean over irradiance and CE group duration"}
knitr::include_graphics("../images/P-groups-bin2d-1.png")
```

@@

```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Distribution of "}
knitr::include_graphics("../images/clim_ECE_month_norm_MAX_median_N-2.png")
```

@@

>>>>

```{r relative-month-occurancies, echo=FALSE, fig.cap="Seasonal statistics of the number of CE occurancies for each month, normalized to the maximum occurancies on June. The box represents the values of the low $25\\,\\%$ percentile to $75\\,\\%$ percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean."}
knitr::include_graphics("../images/clim_CE_month_norm_MAX_median_N-2.png")
```
<!--
```{r echo=FALSE, fig.cap="Distribution of the number of CE cases"}
knitr::include_graphics("../images/climCEmonth-1.png")
```
--->

@@

The relation between the duration and the mean OIR intensity of the groups have been
studied (Figure\nobreakspace{}\ref{fig:group-2d}). We observe that the GCE events
tend to have either long duration, or large intensity, events with strong enhancement
and long duration are very rare. A similar result on this relation, have been also
reported by @Zhang2018, on a study using a far higher sampling rate than ours.

```{r group-2d, echo=FALSE, fig.cap="Relation of mean over irradiance and CE group duration"}
knitr::include_graphics("../images/P-groups-bin2d-1.png")
```

@@

```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Seasonal statistics of the number of ECE occurancies for each month, normalized to the maximum occurancies on March. The box represents the values of the low $25\\,\\%$ percentile to $75\\,\\%$ percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean."}
knitr::include_graphics("../images/clim_ECE_month_norm_MAX_median_N-2.png")
```

@@

Created a clear sky approximation and a long term change representation for a period of 30 years.

Identify CE events and found a trend on .....
The climatology of CE occurrences over the whole period and
the magnitude of the CE events.
We estabished the occurances of extreme CE events ...
